---
title: "dippelmax_OriginalHomeworkCode_05"
author: "Max Dippel"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

monkey <- read.csv("KamilarAndCooperData.csv", header = TRUE)

```

[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).


```{r}
lm1 <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = monkey)

summary(lm1)
# B0(intercept) = -9.44123
# B1(slope) = 1.03643

```


[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
```{r}

boot_intercept <- NULL
boot_slope <- NULL

for (i in 1:1000) {
  #Creating a resampled dataset from the sample data
  sample <- monkey[sample(1:30, replace = TRUE), ]
  
  #Running the regression on these data
  lm_boot <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = sample)
  
  #Saving the coefficients
  boot_intercept <-
    c(boot_intercept, lm_boot$coefficients[1])
  
  boot_slope <-
    c(boot_slope, lm_boot$coefficients[2])
}


```

Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
```{r}

i_se <- sd(boot_intercept)
s_se <- sd(boot_slope)

hist(boot_intercept)

quantile(boot_intercept, c(0.025, 0.975))
quantile(boot_slope, c(0.025, 0.975))


```



How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
```{r}

# SE lm intercept: 0.67293
# SE boot intercept: 2.453888
# SE lm slope: 0.08488
# SE boot slope: 0.2874

# Both the estimates from bootstrapping are larger than from the lm
```

How does the latter compare to the 95% CI estimated from your entire dataset?
```{r}
confint(lm1)
#
#                               2.5 %    97.5 %
# (Intercept)                -10.7720889 -8.110374
# log(Body_mass_female_mean)   0.8685707  1.204292

# Confidence intervals for boot
#              2.5%      97.5% 
# Intercept: -17.317266  -8.595155 
# Slope:     0.8775276 1.9306609 

# The bootstrap confidence intervals have a larger range for both
# the intercept and the slope
```


EXTRA CREDIT
Write a FUNCTION that takes as its arguments a dataframe, “d”, a linear model, “m” (as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level, “conf.level” (with default = 0.95), and a number of bootstrap replicates, “n” (with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.

```{r}
# I'll save this for next week
```


EXTRA EXTRA CREDIT

Graph each beta value from the linear model and its corresponding mean value, lower CI and upper CI from a bootstrap as a function of number of bootstraps from 10 to 200 by 10s. HINT: the beta value from the linear model will be the same for all bootstraps and the mean beta value may not differ that much!

```{r}
# I'll save this for next week
```



